Intervention Bandits

### 2015-01-22 causal-bandit/c-bandit.tex
regret bound for observe until plausible set smaller than alpha
attempted implementation of information direced sampling

@@

Lets try to analyse a very simple model in which the reward depends only on the value of $X_1$.

>>>>

\subsection{Regret during UCB stage}

On completion of the observe stage we have tight bounds on all the arms except the first $\alpha$

Essentially, we want to know how large the regret is if we initialize with a certain number of counts already in place...

\subsection{General rough thoughts}

When observing the confidence interval on all the arms drops approximately with $\sqrt{\frac{1}{n}}$ (provided that the probability of each occurring is the same) - otherwise for each arm it will be weighted by this drop will be weighted by a function of the probability that it occurs. When acting, the interval on a single arm we intervene on drops. What is the informational value of reducing the bounds on various arms (it is higher for arms that are more likely to be good).

@@

But this is just the expected number of steps until one arm does not overlap. With more arms its more complicated - as we need the probability that $\alpha$ of them overlap (another union bound?).
Lets try to analyse a very simple model in which the reward depends only on the value of $X_1$.
